Visualizations for the manuscript

### 2022-10-18 metanalysis_visualization/manuscript_Figures.Rmd
seed added
aesthestics edit on sex plot

```{r}
bootstrap_size <- 10000
binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

@@

```{r }
bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  ggplot(aes(x = time, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(x = time + 0.5, color = period), alpha = 0.01) +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = interaction(quantiles, period)),
            data = filter(quantile_bootstrapped_fitted_sex, sex == "female" & quantiles %in% c("2.5%", "97.5%")),
            linetype = "dashed") +
  geom_line(aes(x = time + 0.5, 
                y = value,
                group = period),
            data = filter(quantile_bootstrapped_fitted_sex, sex == "female" & quantiles == "50%")) +
  geom_point(aes(x = time + 0.5, y = percentage, group = NULL),
             data = filter(patients_hospitalized_agg_sex_total, sex == "female"),
             alpha = 0.5) +
  scale_x_continuous(breaks = breaks_width(1),
                     labels = time_to_time_p, 
                     limits = c(2, 29),
                     expand = c(0.03,0)) + 
  geom_vline(xintercept = 16, linetype = 6 ) +
  scale_colour_manual(values = cbPalette) +
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  scale_colour_manual(values = cbPalette, labels = c("pre-pandemic", "pandemic"), name = "Period") +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
             x = -Inf,
             y = +Inf,
             hjust = 0,
             vjust = 1,
             size = 4,
             inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x =element_blank(),
        axis.title.y = element_text(size = 10),
         panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom")

ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

>>>>

```{r}
bootstrap_size <- 10000
set.seed(1)

binom_proportion <- function(n, prob, size) {
  (rbinom(n, size, prob) / size) * 100
}

@@

```{r }
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b %Y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  labs(
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))

ggsave(plot = plot_sex, filename = "figure4_ITS_sex.png", height = 15, width = 20, units = "cm")
```
